Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-13 firstPaper/corrections/replyToReferee.txt

* def 3.4: do you mean ``any strict subset''?

  Reply: Yes, fixed.

* def 3.16 and others: $\mathcal{S}$ and $S$ are not easily distinguishable

  Reply: We changed it with $\mathbb{S}$ which seems more different.

@@

* Example 3.36: Figure 34 does not illustrate $\omega$

  Reply: We have deleted this example.

* Example 3.44: It appears to me that the map, which is not explicit, is on the
  quotient of $Bic$

  Reply: We have made the sentence of Example 3.44 more precise.

@@

* remark 3.72: do you mean ``Figure 36 (bottom)''?

  Reply: Indeed.

A note about notation. This article uses a quite creative notation set. For
example the blossoming quiver has a little flower as exponent and the operation
of blinding is represented by two half circle to suggest blinkers. I am not sure
I am happy about these choices but I do not have better suggestions to offer.

  Reply: While we agree that the notation set is unconventional, we believe
         that it fits well with our chosen terminology.  We thus respectfully 
         propose to keep the notation as it is.

### 2018-09-07 firstPaper/firstPaperShort/nonKissingComplex.tex
update figure

\enlargethispage{.2cm}
Throughout the paper, we will illustrate our results with two specific families of gentle bound quivers:

@@

We now define and study first elementary properties of the non-kissing complex of a quiver.
This section is inspired from previous works on grid bound quivers~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville}.

@@

Assume for the sake of contradiction that there is~$\lambda \in F$ such that~$\lambda$ and~$\mu$ are kissing.
Let~$\tau$ be a maximal common substring of~$\lambda$ and~$\mu$ where they kiss.
Since~$\lambda$ does not kiss~$\omega$ nor~$\nu$ (as they all belong to~$F$), we obtain that~$\tau$ contains~$v$ and strictly contains~$\sigma$.
%To prove this claim, observe first that~$\mu$ is non-kissing with~$\omega$ and~$\nu$ (since~$\omega$ and~$\nu$ are non-kissing).
%Consider another walk~$\lambda \in F$ and assume that~$\lambda$ and~$\mu$ are kissing.
%Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
We now distinguish two cases (see \fref{fig:pure}\,(right)):
\begin{enumerate}[(i)]
\item If~$\lambda$ passes through~$\beta$, then it enters~$\tau$ with an outgoing arrow (since it kisses~$\mu$), contradicting the maximality of~$\omega$~in~$\prec_\beta$.
\item If~$\lambda$ passes through~$\gamma$, then it enters~$\sigma$ with an incoming arrow (since~$\tau$ strictly contains~$\sigma$), contradicting the maximality of~$\nu$ in~$\prec_\gamma$. 
\end{enumerate}
We obtained a contradiction in all cases, which shows that~$\mu$ is non-kissing with any other walk~of~$F$.

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{pure}}
	\caption{A schematic illustration of the proofs of Lemma~\ref{lem:distArrowExist} and Proposition~\ref{prop:distinguishedArrows}: for each arrow~$\alpha$ on~$\omega$, there is a distinguished arrow on~$\omega$ in the direction of~$\alpha$ (left), and~$\omega$ cannot have two distinguished arrows~$\alpha, \beta$ in the same direction (right). See the proof of Proposition~\ref{prop:distinguishedArrows} for a detailed description.}
	\label{fig:pure}
\end{figure}
\end{proof}

@@

Using material from Part~\ref{part:lattice}, we will characterize distinguishable strings of~$\bar Q$ in Section~\ref{subsec:distinguishableStrings}.

\medskip
We close this section by a technical lemma about distinguished arrows, which will be helpful to understand the different possible situations in Proposition~\ref{prop:flip}.

@@

Assume first that $r$ and $s$ are positive.
Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma' \beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
Thus, $\xi$ is at the bottom of $\sigma''$ and $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.

>>>>

\enlargethispage{.8cm}
Throughout the paper, we will illustrate our results with two specific families of gentle bound quivers:

@@

\enlargethispage{.2cm}
We now define and study first elementary properties of the non-kissing complex of a quiver.
This section is inspired from previous works on grid bound quivers~\cite{PetersenPylyavskyySpeyer, SantosStumpWelker, McConville, GarverMcConville}.

@@

Assume for the sake of contradiction that there is~$\lambda \in F$ such that~$\lambda$ and~$\mu$ are kissing.
Let~$\tau$ be a maximal common substring of~$\lambda$ and~$\mu$ where they kiss.
Since~$\lambda$ does not kiss~$\omega$ nor~$\nu$ (as they all belong to~$F$), we obtain that~$\tau$ contains~$v$ and strictly contains~$\sigma$.
%To prove this claim, observe first that~$\mu$ is non-kissing with~$\omega$ and~$\nu$ (since~$\omega$ and~$\nu$ are non-kissing).
%Consider another walk~$\lambda \in F$ and assume that~$\lambda$ and~$\mu$ are kissing.
%Note that the maximal common substring~$\tau$ of~$\omega$ and~$\lambda$ containing~$v$ is non-empty (otherwise~$\lambda$ would kiss~$\omega$ or~$\nu$) and contains strictly~$\sigma$ (otherwise~$\lambda$ would kiss~$\nu$).
We now distinguish two cases (see \fref{fig:pure}\,(right)):
\begin{enumerate}[(i)]
\item If~$\lambda$ passes through~$\beta$, then it enters~$\tau$ with an outgoing arrow (since it kisses~$\mu$), contradicting the maximality of~$\omega$~in~$\prec_\beta$.
\item If~$\lambda$ passes through~$\gamma$, then it enters~$\sigma$ with an incoming arrow (since~$\tau$ strictly contains~$\sigma$), contradicting the maximality of~$\nu$ in~$\prec_\gamma$. 
\end{enumerate}
We get a contradiction in all cases, therefore~$\mu$ is non-kissing with any other walk~of~$F$.
%
\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{pure}}
	\caption{A schematic illustration of the proofs of Lemma~\ref{lem:distArrowExist} and Proposition~\ref{prop:distinguishedArrows}: for each arrow~$\alpha$ on~$\omega$, there is a distinguished arrow on~$\omega$ in the direction of~$\alpha$ (left), and~$\omega$ cannot have two distinguished arrows~$\alpha, \beta$ in the same direction (right). See the proof of Proposition~\ref{prop:distinguishedArrows} for a detailed description.}
	\label{fig:pure}
\end{figure}
\end{proof}

@@

\enlargethispage{.3cm}
Using material from Part~\ref{part:lattice}, we will characterize distinguishable strings of~$\bar Q$ in Section~\ref{subsec:distinguishableStrings}.
We close this section by a technical lemma about distinguished arrows, which will be helpful to understand the different possible situations in Proposition~\ref{prop:flip}.

@@

Assume first that $r$ and $s$ are positive.
Then $\tau M(\sigma')$ is given by the string $\sigma''=\alpha_{r-1} \cdots \alpha_1 \alpha^{-1} \sigma'$ $\beta \beta_1^{-1} \cdots \beta_{s-1}^{-1}$.
Thus, $\xi$ is at the bottom of $\sigma''$ and $\Hom{A} \big( M(\sigma), \tau M(\sigma') \big) \neq 0$.

### 2018-09-07 secondPaper/accordionComplexSurfaces.tex
update figure

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
We note that our dissections are always cellular, while those found in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle algebra.

@@

The following definition generalises the one from \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  A very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the name ``permissible~arc''.

>>>>

Conversely, the construction of a surface associated to a gentle algebra has appeared in \cite{OpperPlamondonSchroll}.
We give a different construction of the same surface in this paper, which is obtained by ``glueing'' quadrilaterals to the arrows of the blossoming quiver (as defined in \cite{PaluPilaudPlamondon}, and called ``framed quiver'' in \cite{BrustleDouvilleMousavandThomasYildirim}).
Our construction has the advantage that it easily yields the two dual dissections of the surface at the same time (the dissection and dual lamination of \cite{OpperPlamondonSchroll}).
Note that our dissections are always cellular, while those in \cite{BaurCoelhoSimoes} can be arbitrary.
Remarkably, gentle algebras and surfaces were linked recently in \cite{HaidenKatzarkovKontsevich, LekiliPolishchuk}, where the Fukaya category of the surface is shown to be equivalent to the bounded derived category of the associated gentle~algebra.

@@

The following definition generalises the one of \cite{MannevillePilaud-accordion} for the case where~$\bar \surface$ is a disk.  A~very similar definition appears in \cite{BaurCoelhoSimoes} in a slightly different context under the \mbox{name ``permissible~arc''}.
